---
title: "Lab 00 - Hello IDS!"
author: "CATHY"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Cathy Li", "Yanyi Chen", "Ziwei Huang", 
           "Nanshuyuan Zhang"),
  github_username = c("Cathy0804", "yanyi-c", "vivizhere", 
                      "znsy1219"), 
  colour = c("red", "green", "blue", 
             "green"),
  hobby = c("baldursgate", "drama", "drawing", 
            "computergames"),
  favourite_number = c(10, 7, 8, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*The y-axis shows the magnitude of the favourite numbers of each teammate. The ID of each teammate is located at the x-axis and the ID with a larger favourite number comes first. The colour of the bar indicates the favourite colour of each teammate.* 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "the ID of each teammate", 
          y = "the magnitude of the favourite numbers",
          title = "The favourite colour and number of each teammate")
```

*labs() means labels, so it labels the plot, including x-axis, y-axis and the title.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Bar chart is not suitable for this type of data because all users may have different options. Frequency is not very meaningful in this case (but bar chart is good for showing frequency). I would rather use a form to present the data.*
